---
title: "Lijia Yu's resume"
author: Alicia Nortje-da Conceicao
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: TRUE
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}
source("./src/src_functions.R")
source("./src/libraries.R")
data_list <- r_cv_getfilelist()
```


Aside
================================================================================

Contact Info {#contact}
--------------------------------------------------------------------------------

```{r, echo = FALSE, warning = FALSE, message = FALSE}

if (match("contact_info", tolower(names(data_list)))>0) {
  index <- match("contact_info", tolower(names(data_list)))
  data_contact_info <- unlist(data_list[[index]],",")
}
```


- <i class="fa fa-envelope"></i> `r data_contact_info[[grep("email", tolower(names(data_contact_info)))]]`
- <i class="fa fa-linkedin"></i> `r data_contact_info[[grep("linkedin", tolower(names(data_contact_info)))]]`
- <i class="fa fa-phone"></i> `r data_contact_info[[grep("cellphone", tolower(names(data_contact_info)))]]`
- For more information, please contact me via email.


Skills {#skills}
--------------------------------------------------------------------------------

```{r, echo = FALSE, warning = FALSE, message = FALSE}

if (match("skills", tolower(names(data_list)))>0) {
  index <- match("skills", tolower(names(data_list)))
  data_skills <- unlist(data_list[[index]],",")
}
```

<font size="2">

- `r data_skills[grep("skill1", tolower(names(data_skills)))]`

- `r data_skills[grep("skill2", tolower(names(data_skills)))]`

- `r data_skills[grep("skill3", tolower(names(data_skills)))]`

- `r data_skills[grep("skill4", tolower(names(data_skills)))]`

- `r data_skills[grep("skill5", tolower(names(data_skills)))]`

- `r data_skills[grep("skill6", tolower(names(data_skills)))]`

- `r data_skills[grep("skill7", tolower(names(data_skills)))]`

</font size="2">
Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

Last updated on `r Sys.Date()`.



Main
================================================================================

Alicia Nortje-da Conceicao {#title}
--------------------------------------------------------------------------------
```{r, echo = FALSE, warning = FALSE, message = FALSE}
if (match("bio", tolower(names(data_list)))>0) {
  index <- match("bio", tolower(names(data_list)))
  data_skills <- unlist(data_list[[index]],",")
}
```

### `r data_skills[[grep("tagline", tolower(names(data_skills)))]]` 

`r data_skills[[grep("description", tolower(names(data_skills)))]]` 



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

### Univeristy of Cape Town

PhD in Psychology (Eyewitness memory and face recognition)

Cape Town, South Africa

2018

Thesis: Dyadic wavelet and its application in edge detection

+	Completed Masters-level course: Multivariate Statistical Methods (2013)

### University of Cape Town

MA in Psychology Research

Cape Town, South Africa

2011

Thesis: 

+ Completed Clinical Neuropsychology coursework

+ Concurrently registered in undergraduate Linguistics (average 85%) through UNISA

### University of Cape Town

Honours in Psychology Research

Cape Town, South Africa

2007

Thesis: 

### University of South Africa

Bachelors Degree in Psychological Counselling

Cape Town, South Africa

2007

Thesis: 


Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------

### Graduate Research Assistant

Beijing Institute of Genomics, Chinese Academy of Sciences

Beijing, China

2011 - 2014

- Performed computational biology research towards understanding regulation of alternative splicing in human and mouse transcriptome.
- Found EGFR pathway related mutations, aimed to understand the impacts of cancer mutations on EGFR signaling pathway.

### Bioinformatican

My Health Gene Technology Co., Ltd.

Beijing, China

2015 - 2016

- Investigated how cancer cells spread to other parts of the body at the single cell level.

### Visiting Scientist

University of Alabama at Birmingham

AL, USA

2016 - 2018

- Investigated the role of mitochondria in development of cancer.
- Investigated the evolution of genome architecture and its role in important evolutionary events.
- Detected thrombotic thrombocytopenic purpura related mutations in mutiple patients' blood genome.
  

Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

### Data Scientist, intern

SupStat Inc.

Beijing, China

2014

::: concise
- Taught R language to beginners. 
- Wrote Shiny app demos.
- Converted statistical tutorials from SPSS to R language.
:::

### Bioinformatician

My Health Gene Technology Co., Ltd.

Beijing, China

2015 - 2016

::: concise
- Analyzed whole-exome sequencing data. 
- Wrote analysis pipelines of ChIP-seq, single cell DNA-seq and single cell RNA-seq.
- Studied tumor metastasis and wrote research reports. 
- Also did case studies to identify the genetic defect causing rare disease.
:::


Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

### Introduction to R Language for Beginners.

Instructor of R and Data Mining Training Courses at SupStat Inc.

Beijing, China

2014

### Computational Biology and Bioinformatics.

Teaching assistant of GBS CB2-201 courses at UAB

AL, USA

2016 - 2017


Selected Publications and Posters {data-icon=file}
--------------------------------------------------------------------------------

### Genetic and epigenetic signals are found predictive to the distribution of intra-individual divergence of alternative splicing.

Poster for 2013 International Conference of Genomics

Qingdao, China

2014

**Yu L**, Chen B, Zhang Z.

### ESCRT-0 complex modulates Rbf mutant cell survival by regulating Rhomboid endosomal trafficking and EGFR signaling.

J Cell Sci. 2016 May 15;129(10):2075-84.

N/A

2016 

Sheng Z, **Yu L**, Zhang T, Pei X, Li X, Zhang Z and Du W. 
